```{r,echo=FALSE,results='hide',message=F, warning=F}
  library(dplyr)
library(stringr)
  ### - TODO
  ### Update varaible g_session to reflect the session being processed
  g_session <- "201511" 
  
```
---
title: "IONIN24H - `r g_session` Session Summary" 
author: "Aasish Agarwal"
---
#### `r date()`

```{r,echo=FALSE,results='hide'}
## Defining Constants and functions

g_data_root <- "data/sessions"
g_miling_list_folder <- "teams"
g_verbose_output_folder <- "verbose"
g_team_groups_file <- "team_groups.csv"
g_innovators_file <- "innovators.csv"
g_voters_file <- "voters.csv"
g_ion_contacts_file <- "ion_contacts.csv"

# Prepare Participant Structure
## Browse through the list of teams
## Create a data frame with mail id and mailing list name
read_mailing_lists <- function(session) 
{
  mailinglistpath = paste( g_data_root , session , g_miling_list_folder , sep = "/")
  files <- list.files(path=mailinglistpath, pattern="*.txt", full.names=T, recursive=FALSE)
  
  mailing_lists <- do.call(rbind,lapply(files, function(x) {
    listname <- sub("@.*", "", basename(x))
    members <- read.csv(x,stringsAsFactors = F, na.strings=c("NA","NaN", "") , header = F) %>%
      tbl_df() %>%
      filter( !is.na(V1) ) %>%
      mutate(email = sub(".*<", "", V1), email = sub(">.*","",email),team = listname)  %>%
      mutate(email = str_trim(email)) %>%
      mutate(email = tolower(email))  %>%
      select(email,team)
    })
  )
  return(mailing_lists)
}

# load team groups
read_team_groups <- function(session) 
{
  filename = paste( g_data_root , session , g_team_groups_file , sep = "/")
  team_groups <- read.csv(filename,stringsAsFactors = F, na.strings=c("NA","NaN", "") ) %>%
    tbl_df()
  
  return(team_groups)
}

# load innovators
read_innovators <- function (session) 
  {
  filename = paste( g_data_root , session , g_innovators_file, sep = "/")
  innovators <- read.csv(filename,stringsAsFactors = F, na.strings=c("NA","NaN", "") ) %>%
    tbl_df() %>%
    mutate(email = tolower(email), innovated = 1)  %>%
    mutate(email = str_trim(email)) %>%
    unique()
  
  return(innovators)
}

# Prepare voters list
read_voters <- function (session)
{
    filename = paste( g_data_root , session , g_voters_file, sep = "/")
  voters <- read.csv(filename,stringsAsFactors = F, na.strings=c("NA","NaN", "") ) %>%
    tbl_df() %>%
    rename(email = Username) %>%
    select(email) %>%
    filter( !is.na(email) ) %>%
    mutate(email = str_trim(email)) %>%
    mutate(email = tolower(email), voted = 1) 
  
  return(voters)
}

# Create the data frame with mail, Location, Team, Group
## Read the contacts file
read_ion_contacts <- function(session) 
{
  filename = paste(g_data_root , session , g_ion_contacts_file , sep = "/")
  ion_contacts <- read.csv(filename,stringsAsFactors = F, na.strings=c("NA","NaN", "") ) %>%
    tbl_df() %>%
    rename(email = E.mail.Address , location = Office.Location) %>%
    select(email,location,Company,Department) %>%
    filter( !is.na(email) ) %>%
    mutate(email = tolower(email))  
  return(ion_contacts)
}


## Export to CSV
export_to_csv <- function (data , fname) {
  #g_data_root <- "data/sessions"
  #g_verbose_output_folder <- "verbose"
  
  berbose_root <- paste( g_data_root , g_session , sep = "/")
  dir.create(file.path(berbose_root, g_verbose_output_folder), 
             showWarnings = FALSE)
  fname_verbose = paste( berbose_root , g_verbose_output_folder , fname, sep = "/")

  write.table(data, fname_verbose,row.names=F,sep=",")
}


## Prepare Master Data Frame
prepare_master_data_frame <- function(session, mailing_lists, team_groups, innovators, voters, ion_contacts ) 
{
  report_df <- merge(mailing_lists, voters, by="email", all.x=TRUE) %>% tbl_df()
  report_df <- merge(report_df, ion_contacts, by="email", all.x=TRUE) %>% tbl_df()
  report_df <- merge(report_df, team_groups, by="team", all.x=TRUE) %>% tbl_df()
  report_df <- merge(report_df, innovators, by="email", all.x=TRUE) %>% tbl_df()
  report_df$innovated = replace(report_df$innovated, is.na(report_df$innovated), 0)
  report_df$voted = replace(report_df$voted, is.na(report_df$voted), 0)
  
  export_to_csv (report_df, "report_df.csv") 

  return(report_df)
}


```


```{r,echo=F}
# Preparing data set

mailing_lists <- read_mailing_lists(g_session)
team_groups <- read_team_groups(g_session) 
innovators <- read_innovators(g_session) 
voters <- read_voters(g_session)
ion_contacts <- read_ion_contacts(g_session)

report_df <- prepare_master_data_frame(g_session, mailing_lists, team_groups, innovators, voters, ion_contacts ) 


```
# Reconciliation
```{r,echo=F}
reconsile_voting <-  function (report_df , voters) {
  # Mail sent to 
    total_members <- nrow(report_df %>%
    filter( !is.na(location) ) %>%
    select(email) %>%
    unique() )

  # Total members voted
    total_voted <- nrow(voters)

  # Members who voted from the mailing list
    invitees_voted <- nrow(report_df %>%
    filter( !is.na(location) , voted > 0 ) %>%
    select(email) %>%
    unique() )
    
  # Members not in the mailing lists that voted
    A <- unique(report_df$email)
    B <- unique(voters$email)
    noninvitees_voted <- length( B[which(!B %in% A)])

  # Members who voted but are not in ION contacts
    notincontacts_voted <- nrow(report_df %>%
    filter( is.na(location) , voted > 0 ) %>%
    select(email) %>%
    unique())
    
    return (data.frame(Total = c(total_members), 
                       voted = c(total_voted),
            Invited = c(invitees_voted),
            NotInvited = c(noninvitees_voted),
            NotInContacts = c(notincontacts_voted)))
}

knitr::kable(reconsile_voting(report_df = report_df, voters = voters))
```

# Participation By Location
This section summarizes the members at different Geographical Locations. Same is also exported in `voting_by_location.csv` 



```{r, echo = F}

summarize_voting_by_location <- function (report_df) 
{
  report_df_for_location <- report_df %>%
    select(email,voted,location) %>%
    filter( !is.na(location) ) %>%
    unique() %>% 
    group_by(location) %>%
    summarize(count = n(), total = sum(voted), pct  = round((total/count)*100,0)) %>%
  filter(pct > 0) %>%
    arrange(pct)
  
  export_to_csv (report_df_for_location %>% mutate(pct=pct/100),
    "voting_by_location.csv") 

  return(report_df_for_location)
}

knitr::kable(summarize_voting_by_location(report_df = report_df))
```

# Participation By Area
This section presents the summary of people who voted from different area like CAT, XTP etc.Same is also exported in `voting_by_area.csv` 

```{r, echo=F}
summarize_voting_by_area <- function (report_df) 
{
  report_df_for_area <- report_df %>%
    filter( !is.na(location) ) %>%
    select(email,area,voted) %>%
    unique() %>%
    group_by(area) %>%
    summarize(count = n() , total = sum(voted), 
              pct  = round((total/count)*100,0) ) %>%
    arrange(pct)
  
  export_to_csv(report_df_for_area %>% mutate(pct=pct/100),
    "voting_by_area.csv")

  return(report_df_for_area)
}


knitr::kable(summarize_voting_by_area(report_df = report_df))

```

# Summary Of Members Who Presented Their Projects
Same is also exported in `innovators_summary.csv` along with the full list of innovators in `innovator_list.csv`

```{r, echo=F}
summarize_innovators <- function(report_df) 
{
  report_df_for_innovators <- report_df %>%
    select(email,area,team,innovated,location) %>%
    filter( !is.na(location) ) %>%
    unique() %>%
    group_by(area,team) %>%
    summarize(count = n() , total = sum(innovated) )  %>%
    filter (total >0 ) %>%
    arrange(area, team)
  
  export_to_csv(report_df_for_innovators, "innovators_summary.csv")
  return(report_df_for_innovators)
}


export_innovator_list <- function(report_df) 
{
  
  innovator_list <- report_df %>%
    select(email,area,team,innovated)  %>%
    filter ( innovated > 0) %>% 
    select (area, team, email ) %>%
    arrange(area, team, email)

    export_to_csv(innovator_list, "innovator_list.csv")
}


knitr::kable(summarize_innovators( report_df = report_df ))

export_innovator_list(report_df = report_df) 
```

# Potential Participants
These are the people who participated in voting, bue there names were not in one of the mailing lists that we sent the invitation to.

Same is also exported in `potential_participants.csv`

```{r, echo = F}
get_potential_participants <- function (voters, report_df) 
{
  all_that_voted <- select(voters,email)
  all_that_voted_from_mailing_lists <- report_df %>%
    select(email,voted) %>% filter(voted > 0) %>% unique()
  
  potential_participants <- merge(x= all_that_voted ,     
    all_that_voted_from_mailing_lists, by="email", all.x=TRUE) %>% 
    tbl_df() %>% 
    filter(is.na(voted)) %>% select(email)
  
  export_to_csv(potential_participants,
      "potential_participants.csv")

  return(potential_participants)
}


knitr::kable(get_potential_participants (voters = voters, report_df = report_df) )

```


# Correction Required In Mailing Lists
This is the list of people who are in our mailing lists but they are not in ION anymore. We can use this list to follow up correction in mailing lists. 

Export for same is available in the work folder as a CSV file - `people_who_left.csv`.

```{r, echo=F}
get_list_for_correction <- function (report_df) {
  people_who_left <- report_df %>%
    filter( is.na(location) ) %>%
    select(area,team,email) %>%
    arrange(area,team)

  export_to_csv(people_who_left, "people_who_left.csv")
  return(people_who_left)
}

tonull <- get_list_for_correction(report_df = report_df)
```

# Preparing This Report
This script assumes that data for analysis is stored under `data\sessions` folder.

* Create a folder named `<yyyymm>` under sessions folder - `Working Folder`
* Download the contacts from `ION Tracker` and save them as `ion_contacts.csv` in `Working Folder`
* Create `voters.csv` in `Working Folder` from the responses recieved for this session. Only include the `Username` column
* Create `team_groups.csv` in `Working Folder` capturing the relationship of a team with area, so that we can produce area wise summary. Having columns `team	and area`. 
* * Example `anvil9ba,	Anvil`
* Create `innovators.csv` in `Working Folder` listing email of all members that presented their projects. Column must have the header `email`

# Notes
Exoported CSV files are available in:

<h4>
`r paste( getwd(),g_data_root , g_session, g_verbose_output_folder , sep = "/")`
</h4>
